---
title: "HeatMap Exploration"
author: "John Little"
date: "`r Sys.Date()`"
output: html_notebook
---

## Get Special Libray Packages.

Examples of interactive HTMLwidgets can be found in the [widget gallery](http://gallery.htmlwidgets.org/).  Recommend browsing with "CRAN Only" set to FALSE, and Tag = "heatmap".

The top three packages include:  `d3heatmap`, and `heatmaply`. 

Another good option for stylized interactive charts are the [plotly package](https://plot.ly/r/) (includes `ggplotly()` which can be used with `ggplot2::geom_tile()`) and the [HighCharter package](http://jkunst.com/highcharter/).

In the example below, install `d3heatmap`.  Do this one time for each R/Rstudio instance.  Check console for interactive install questions.

```{r}
if(!require(d3heatmap)) {
  devtools::install_github("rstudio/d3heatmap")
}
```


## Load Library Packages

```{r}
library(tidyverse)
library(d3heatmap)
```

```{r}
d3heatmap(mtcars, scale = "column", colors = "Spectral")
d3heatmap(mtcars[1:4,], scale = "column", colors = "Blues")

starwars %>% 
  column_to_rownames("name") %>% 
  select_if(is.numeric) %>% 
  drop_na() %>%
  d3heatmap(scale = "column",
            colors = "Greens")

```




```{r}

```

